### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@87f717c2b1cd34f55b3125064f042bb5f54eacd4 🚀

Having a general solution for inferring \emph{potential} interactions
(despite the unavailability of interaction data) could be the catalyst
for significant breakthroughs in our ability to start thinking about
species interaction networks over large spatial scales. In a recent
overview of the field of ecological network prediction, Strydom et al.
(2021) identified two challenges of interest to the prediction of
interactions at large scales. First, there is a relative scarcity of
relevant data in most places globally -- paradoxically, this restricts
our ability to infer interactions to locations where inference is
perhaps the least required; second, accurate predictions often demand
accurate predictors, and the lack of methods that can leverage small
amount of data is a serious impediment to our predictive ability
globally.

@@

>>>>

Having a general solution for inferring \emph{potential} interactions
(despite the unavailability of interaction data) could be the catalyst
for significant breakthroughs in our ability to start thinking about
species interaction networks over large spatial scales (Hortal et al.,
2015). In a recent overview of the field of ecological network
prediction, Strydom et al. (2021) identified two challenges of interest
to the prediction of interactions at large scales. First, there is a
relative scarcity of relevant data in most places globally --
paradoxically, this restricts our ability to infer interactions to
locations where inference is perhaps the least required; second,
accurate predictions often demand accurate predictors, and the lack of
methods that can leverage small amount of data is a serious impediment
to our predictive ability globally.

@@

\leavevmode\hypertarget{ref-Hortal2015SevSho}{}%
Hortal, J., de Bello, F., Diniz-Filho, J. A. F., Lewinsohn, T. M., Lobo,
J. M., \& Ladle, R. J. (2015). Seven Shortfalls that Beset Large-Scale
Knowledge of Biodiversity. \emph{Annual Review of Ecology, Evolution,
and Systematics}, \emph{46}(1), 523--549.
\url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}
